---
title: "BZAN 542-CSGO"
author: "Group 8"
date: "2022-12-12"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Loads in the data and packages needed.
```{r}
#Change the working directory to your own.
setwd("C:/Users/liana/Downloads/archive")

#Loads in the required packages
library(tidyverse)
library(dplyr)
library(reshape2)

# Read in and combine the two .csv files containing the by-event damage data
csgo_data <- rbind(read.csv("esea_master_dmg_demos.part1.csv"), 
             read.csv("esea_master_dmg_demos.part2.csv"))

# Read in the win data for the matches
csgo_win_data <- rbind(read.csv("esea_meta_demos.part1.csv"), read.csv("esea_meta_demos.part2.csv")) 

```

Finds the column names and how the games are grouped in the dataset.
```{r}

colnames(csgo_data)

files_names <- unique(csgo_data$file) #each file is a separate ESEA match with all of its associated data
```



Creates unique identities for each player in each match that stays through each round so we can document hp.
```{r}
player_round_map <- csgo_data %>%
                    select(file, round, vic_side, vic_id) %>%
                    distinct() %>% #eliminates repeats of the exact same row where rows are identical
                    group_by(file, round, vic_side) %>% #groups by the match, round, then victim side that was shot
                    mutate(pnumber = row_number()) %>% #makes a column called pnumber which is th row number
                    mutate(player_id = paste0(vic_side, pnumber)) %>% #combines the two string names together to make the names for the players
                    ungroup() %>% #ungroups items to delete stuff
                    select(-pnumber, -vic_side) %>% #deletes pnumber and vic_side columns because we have player_id now
                    spread(player_id, vic_id) %>% 
                    select(file,
                           round,
                           CounterTerrorist1,
                           CounterTerrorist2,
                           CounterTerrorist3,
                           CounterTerrorist4,
                           CounterTerrorist5,
                           Terrorist1,
                           Terrorist2,
                           Terrorist3,
                           Terrorist4,
                           Terrorist5)
```


Creates a table which documents the damage taken by each player for each round of each match
```{r}
tagged_dmg_data <- csgo_data %>%
                   left_join(player_round_map, by=c('file','round')) %>% #combines the new table with full table data by round=file
                   rowwise() %>%
                   mutate(CounterTerrorist1Dmg = if(vic_id %in% CounterTerrorist1) -hp_dmg else 0, #Sorts into each column who the dmg is taken by
                           CounterTerrorist2Dmg = if(vic_id %in% CounterTerrorist2) -hp_dmg else 0,
                           CounterTerrorist3Dmg = if(vic_id %in% CounterTerrorist3) -hp_dmg else 0,
                           CounterTerrorist4Dmg = if(vic_id %in% CounterTerrorist4) -hp_dmg else 0,
                           CounterTerrorist5Dmg = if(vic_id %in% CounterTerrorist5) -hp_dmg else 0,
                           Terrorist1Dmg = if(vic_id %in% Terrorist1) -hp_dmg else 0,
                           Terrorist2Dmg = if(vic_id %in% Terrorist2) -hp_dmg else 0,
                           Terrorist3Dmg = if(vic_id %in% Terrorist3) -hp_dmg else 0,
                           Terrorist4Dmg = if(vic_id %in% Terrorist4) -hp_dmg else 0,
                           Terrorist5Dmg = if(vic_id %in% Terrorist5) -hp_dmg else 0)
```


Makes the damage table be in order of time so players take damage in time order.
```{r}
tagged_dmg_data <- tagged_dmg_data %>% 
                   group_by(file, round) %>% 
                   arrange(tick) %>% #in time order to make sure that the damage is being taken in time order
                   mutate(CT1_health = 100+cumsum(CounterTerrorist1Dmg), #makes it so each combination of each file/match and round
                          CT2_health = 100+cumsum(CounterTerrorist2Dmg), #the 100 is the base health
                          CT3_health = 100+cumsum(CounterTerrorist3Dmg),
                          CT4_health = 100+cumsum(CounterTerrorist4Dmg),
                          CT5_health = 100+cumsum(CounterTerrorist5Dmg),
                          T1_health = 100+cumsum(Terrorist1Dmg),
                          T2_health = 100+cumsum(Terrorist2Dmg),
                          T3_health = 100+cumsum(Terrorist3Dmg),
                          T4_health = 100+cumsum(Terrorist4Dmg),
                          T5_health = 100+cumsum(Terrorist5Dmg))
```


Creates a table that has all the win and loss data and game duration.
```{r}                                                                    
win_data <- csgo_win_data%>%
        mutate(duration=end_seconds - start_seconds) %>% #calculates the duration of each game
        select(-start_seconds, -end_seconds) #deletes the extra columns
```


Combines damange table,win-loss data, and game lengths for each match.
```{r}
#Combines damage data with win loss data for each match and game lengths
tagged_dmg_data <- tagged_dmg_data %>%
                   left_join(win_data, on=c(file, round))
```


Cleans up table.
```{r}
training_data_to_write <- tagged_dmg_data %>%
                          select(-Terrorist1, #Cleans up table for machine learning
                                 -Terrorist2,
                                 -Terrorist3,
                                 -Terrorist4,
                                 -Terrorist5,
                                 -CounterTerrorist1,
                                 -CounterTerrorist2,
                                 -CounterTerrorist3,
                                 -CounterTerrorist4,
                                 -CounterTerrorist5,
                                 -Terrorist1Dmg,
                                 -Terrorist2Dmg,
                                 -Terrorist3Dmg,
                                 -Terrorist4Dmg,
                                 -Terrorist5Dmg,
                                 -CounterTerrorist1Dmg,
                                 -CounterTerrorist2Dmg,
                                 -CounterTerrorist3Dmg,
                                 -CounterTerrorist4Dmg,
                                 -CounterTerrorist5Dmg,
                                 -hitbox,
                                 -att_id,
                                 -vic_id,
                                 -att_rank,
                                 -vic_rank,
                                 -hp_dmg,
                                 -arm_dmg,
                                 -wp,
                                 -wp_type)



```

Adds a column to make the win-loss binary.
```{r}
training_data_to_write <- training_data_to_write %>%
                          mutate(vic_won=(vic_team == winner_team))
```



Makes the csv.
```{r}
#Write data in format for training to .csv
write.csv(training_data_to_write, "C:/Users/liana/BZAN542project/all_game_state_data_bool.csv")
```



